---
output: officedown::rdocx_document
---
```{r, echo=FALSE,include=FALSE}

# Source functions to do forecasts, tables of results, and plots.
source("functions2.R")

# Pull in needed packages.
library(flextable)
library(tidyverse)
library(htmltools)
library(knitr)
library(officedown)
library(officer)
library(readxl)
library(dlm)
library(Metrics)
library(here)

# Print session info at end of document for reproducibility? 
prnt_info <- TRUE

# Pull in brood or return table ####
# This table needs to have headers named exactly, NO SPACES!), but order doesnt matter. 
# ReturnYear (or BroodYear), AgeX1,AgeX2...AgeXmax, Stock
# e.g. the header looks like: ReturnYear | Age2 | Age3 | Age4 | Stock
# If this is a brood table, be sure to specify the na's if they are not just blank cells.
# df <- read_xlsx("klick2019.xlsx",sheet=1)
#df <- read_xlsx("CKL_2019.xlsx", sheet=1)
#df <- read_xlsx("Input_TAC_Forecasting_Spring_Summer_Chinook.xlsx", sheet="ReturnTable")


df <- read_csv("Data/2024/new_return_table_2023.csv") %>%
  mutate(Age6=replace_na(Age6,0),
    Age5=Age5+Age6) %>%
  select(-Age6) %>% 
  filter(Stock %in% c("BPH","LRW", "PUB",  "URB",  "LRH+","LRB")) %>% mutate(Stock=ifelse(Stock=="LRH+","LRH",Stock))
# 
#  df <- df %>% filter(Stock=="BPH") #%>% filter(ReturnYear>=1975)

# 
# df <- readxl::read_xlsx("Spring_Chinook_Returns.xlsx", sheet=1) %>%
#   mutate(Age6=replace_na(Age6,0),
#     # Age6=Age6+1#,
#     Age5=Age5+Age6
#     ) %>%
#   select(-Age6) %>%
#   filter(ReturnYear<=2023) #enter current return year here

# df<-readxl::read_xlsx("Data/2024/Snake W Returns at BON.xlsx",skip=1) %>% `colnames<-`(c("BroodYear" ,"Age3" ,"Age4","Age5")) %>% mutate(Stock="Snake_wild",BroodYear=BroodYear-2) 


#upper C wild
# df <- readxl::read_xlsx("Data/2024/upperC_wild_sprng.xlsx",sheet=1) %>% dplyr::select(ReturnYear,Age3,Age4=Age4) %>% mutate(Stock="Up_C_wild") %>% drop_na()


# df<-readxl::read_xlsx("Data/2024/sockeye.xlsx",sheet="RY")%>% 
#   
#   filter(River=="Wenatchee") %>% 
#   mutate(Age4=Age4+Age3,
#          across(Age3:Age5,function(x)ifelse(x==0,1,x))) %>% rename(Stock=River)


#Sockeye
# df<-readxl::read_xlsx("Data/2024/sockeye.xlsx",sheet="RY")%>%
#   group_by(ReturnYear) %>% summarize(across(Age3:Age5,sum)) %>% pivot_longer(Age3:Age5,names_to = "age",values_to = "n")%>%
#   group_by(ReturnYear) %>% mutate(props=proportions(n)) %>% left_join(readxl::read_xlsx("Data/2024/sockeye.xlsx",sheet="RMRS"),by=c("ReturnYear"="Year")) %>% mutate(n2=props*River_Mouth_Run_Size) %>% select(ReturnYear,age,n2) %>% pivot_wider(names_from = age,values_from = n2) %>% mutate(Stock="Sockeye") %>% mutate(Age4=Age4+Age3)





#  # spring CHinook
#  df <- read_xlsx("Data/2024/UpriverSprings.xlsx",sheet=1) %>%
#     mutate(
#       # Age6=replace_na(Age6,0),
#     # Age5=Age5+lag(Age6)
#     Age6=Age6+1
#     ) %>%
#   # select(-Age6)
# rename(BroodYear=`Brood Year`)
 # 
 # 
 # df <- readxl::read_xlsx("Data/2024/SummerChinook.xlsx",sheet=1) %>%
 #    mutate(Age6=replace_na(Age6,0),
 #               Age6=Age6+1#,
    # Age5=Age5+lag(Age6)
    # ) #%>%
 # select(-Age6)
 # 
 # 
 # df<-bind_rows(upsprngs,up_sums)

 #%>% mutate_at(vars(contains("Age")), ~round(.x*1000))
#df <- read_xlsx("2019LRBReturnTable.xlsx",sheet=1)#%>% mutate_at(vars(contains("Age")),~if_else(.x==0,.001,.x))

# OUTPUT Brood and Return tables for RoundTable
# library(openxlsx)
# rt <- df
# bt <- df %>% return_to_brood()
# 
# write.xlsx(list(Return=rt,Brood=bt),file="2021BroodTables.xlsx") 
# df %>% select(Stock,ReturnYear,Age2,Age3,Age4,Age5,Age6) %>% return_to_brood() %>% write.table("clipboard",row.names=FALSE)

# df<-readxl::read_xlsx(here("Data","2023","Basic Brood Tables for WDFW.xlsx"),sheet="RY") %>%   mutate(across(Age3:Age5,function(x)ifelse(x==0,.5,x))) %>% rename(Stock=River)

# df<-readxl::read_xlsx(here("Data","2023","UpperC_Chk.xlsx"),sheet=1) %>% #select(-Age3) %>%
#   rename(ReturnYear=Year) %>%
#          # Age3=JackHalf) %>%
#   mutate(Stock="Upper_C_SpChk") %>%
#   select(-JackHalf)

  


# df<-readxl::read_xlsx(here("CKL_2019.xlsx"),sheet=1) %>%
#   filter(Stock=="Wind")%>%
    # select(-c(Age3,Age4)) %>% 
# df<-readxl::read_xlsx(here("Data","2023","UpriverSprings.xlsx"),sheet=1)%>%
# # df<-readxl::read_xlsx(here("Data","2023","SummerChinook.xlsx"),sheet=1)%>%
#   #change 0 to .5
  # mutate(across(Age3:Age6,function(x)ifelse(x==0,.5,x)))

# write_csv(df,here("Data","2023","SummerReturns.csv"))


# Do forecasts ####
# table type is either "return" or "brood". Return tables are converted to brood tables.
wt_type<-"RMSE_wt"
o <- do_forecasts(df, table_type="return",n_eval=10,wt_type=wt_type)

# o$Predictions %>% filter(Mod=="constIntOnly",Age==4,BroodYear==2019)
# test<-o$Predictions %>% filter(Mod!="MAPE_wt")%>% mutate(across(c(AICc_wt,MAPE_wt),~.x*Pred_med)) %>% 
#   group_by(ReturnYear,Stock,Age) %>%  summarise(across(c(AICc_wt,MAPE_wt),sum),actual=mean(actual)) %>% group_by(ReturnYear,Stock) %>% summarise(across(c(AICc_wt,MAPE_wt,actual),sum))  %>% drop_na() %>% write.csv("preds.csv")


#o %>% mod_avg_totals(stock = "Cowlitz")
#o %>% mod_avg_totals(stock="LRH")
# Extract stocks/ages and forecast year ####
stocks <- unique(o$ModelSelectionResults$Stock)

ages <- unique(o$ModelSelectionResults$Age)

forecast_year <- o$Predictions %>% 
  # mutate(ReturnYear=BroodYear+Age) %>% 
  pull(ReturnYear) %>% 
  max()

```

---
title: `r forecast_year` Forecasts for `r paste(stocks)`
---

# Model Descriptions
A suite of 8 models are run for each brood table provided.  The 8 models are variants of sibling regressions, cohort ratios, and average returns.

```{r,echo=FALSE}
# Put in table of model descriptions.
read_xlsx("model_descriptions.xlsx",sheet=1) %>% 
  flextable() %>% 
  align(align="left", part="all") %>% 
  autofit()
```

Performance metrics (MSA,RMSE, MAPE), and prediction intervals are based on retrospective one-year-ahead forecasts.

Model averageing was done with `r wt_type`

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE,fig.width=7,fig.height=5,dpi=300,fig.align='center'}
  cat("<br><br><br><br><br>\n\n\n")

for(s in stocks){
  cat('\\pagebreak')
  cat(paste("##", s," returns by age class <br><br>\n\n"))
  print(plot_returns(o, s))
  cat("<!---CHUNK_PAGEBREAK--->\n\n")
    cat('\\pagebreak')
  for (a in ages ){
  # cat('\\pagebreak')
    cat(paste("##",s, "Age",a),"model selection\n\n")
    tbl <- make_mod_sel_tbl(o, stock=s, age=a)
    #tbl
    # If html output
     cat(knit_print(tbl),"<br>","\n\n")
    # If word output
    #  flextable::docx_value(tbl)
      cat("\n\n")
      print(plot_preds(o, stock=s, age=a))
      cat("<!---CHUNK_PAGEBREAK--->\n\n")

  }
    cat('\\pagebreak')
    cat(paste("##", s, "model-averaged forecasts for", forecast_year,"\n\n"))
    # docx_value(mod_avg_totals_ft(o, stock=s))
    # tbl2_dat <- mod_avg_totals_ft2(o,stock=s)
        tbl2 <- mod_avg_totals_ft(o,stock=s)
    cat(knit_print(tbl2),"<br>","\n\n")
    #cat("<br><br>\n\n")
  print(plot_tots(o, stock=s))
 if(prnt_info | s != stocks[length(stocks)]){cat("<!---CHUNK_PAGEBREAK--->\n\n")}
}

```

```{r,echo=FALSE, eval=prnt_info, results='asis'}
# If prnt_info, make a header 
cat("## R Session Info\n\n")
```

```{r, echo=FALSE, eval=prnt_info, comment=NA}
#Paste in the session info
sessionInfo()
```
